Title

### 2024-04-04 latex/draft/draft.tex
fdf

>>>>

Tables for Ali
% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Apr  3 19:45:50 2024
\begin{table}[ht]
    \centering
    \begin{tabular}{rrrrrrlr}
      \hline
     & mean & sd & 2.5\% & 50\% & 97.5\% & sig & abs\_Z \\ 
      \hline
    intercept & 3.66 & 0.53 & 2.70 & 3.64 & 4.77 & TRUE & 6.96 \\ 
      seasonSpring & -0.06 & 0.08 & -0.23 & -0.06 & 0.09 & FALSE & -0.80 \\ 
      seasonSummer & -0.55 & 0.08 & -0.72 & -0.55 & -0.38 & TRUE & -6.50 \\ 
      seasonWinter & -0.24 & 0.10 & -0.42 & -0.23 & -0.05 & TRUE & -2.45 \\ 
      BC & 0.82 & 0.14 & 0.55 & 0.82 & 1.09 & TRUE & 6.00 \\ 
      M & -1.89 & 0.93 & -3.85 & -1.85 & -0.18 & TRUE & -2.03 \\ 
      NB & -2.60 & 1.06 & -4.84 & -2.55 & -0.66 & TRUE & -2.45 \\ 
      NL & -3.04 & 1.13 & -5.43 & -2.98 & -0.99 & TRUE & -2.70 \\ 
      NT & -5.40 & 1.37 & -8.20 & -5.34 & -2.94 & TRUE & -3.94 \\ 
      NS & -2.38 & 1.00 & -4.53 & -2.34 & -0.54 & TRUE & -2.38 \\ 
      N & -4.98 & 1.28 & -7.68 & -4.92 & -2.61 & TRUE & -3.89 \\ 
      O & 5.54 & 2.37 & 1.18 & 5.40 & 10.58 & TRUE & 2.34 \\ 
      PEI & -4.10 & 1.23 & -6.73 & -4.04 & -1.82 & TRUE & -3.32 \\ 
      Q & 2.17 & 0.88 & 0.55 & 2.12 & 4.04 & TRUE & 2.48 \\ 
      S & -2.56 & 0.96 & -4.57 & -2.52 & -0.77 & TRUE & -2.67 \\ 
      Y & -4.11 & 1.26 & -6.77 & -4.06 & -1.81 & TRUE & -3.27 \\ 
      retail & -1.83 & 1.04 & -4.05 & -1.77 & 0.08 & FALSE & -1.76 \\ 
       \hline
    \end{tabular}
    \end{table}

    % latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Apr  3 19:45:51 2024
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrlr}
  \hline
 & mean & sd & 2.5\% & 50\% & 97.5\% & sig & abs\_Z \\ 
  \hline
intercept & 3.68 & 0.51 & 2.68 & 3.68 & 4.69 & TRUE & 7.20 \\ 
  seasonSpring & -0.07 & 0.08 & -0.23 & -0.07 & 0.10 & FALSE & -0.78 \\ 
  seasonSummer & -0.55 & 0.09 & -0.72 & -0.55 & -0.38 & TRUE & -6.35 \\ 
  seasonWinter & -0.23 & 0.09 & -0.41 & -0.23 & -0.05 & TRUE & -2.55 \\ 
  BC & 0.82 & 0.16 & 0.51 & 0.82 & 1.14 & TRUE & 4.98 \\ 
  M & -1.92 & 0.92 & -3.75 & -1.91 & -0.11 & TRUE & -2.08 \\ 
  NB & -2.63 & 1.05 & -4.72 & -2.63 & -0.57 & TRUE & -2.51 \\ 
  NL & -3.08 & 1.11 & -5.31 & -3.06 & -0.89 & TRUE & -2.77 \\ 
  NT & -5.41 & 1.27 & -7.92 & -5.39 & -2.91 & TRUE & -4.24 \\ 
  NS & -2.42 & 1.00 & -4.39 & -2.41 & -0.46 & TRUE & -2.43 \\ 
  N & -5.01 & 1.27 & -7.52 & -5.01 & -2.53 & TRUE & -3.94 \\ 
  O & 5.61 & 2.45 & 0.80 & 5.59 & 10.51 & TRUE & 2.29 \\ 
  PEI & -4.13 & 1.22 & -6.54 & -4.12 & -1.73 & TRUE & -3.39 \\ 
  Q & 2.20 & 0.93 & 0.36 & 2.19 & 4.07 & TRUE & 2.35 \\ 
  S & -2.59 & 0.94 & -4.46 & -2.57 & -0.75 & TRUE & -2.74 \\ 
  Y & -4.15 & 1.25 & -6.61 & -4.14 & -1.71 & TRUE & -3.33 \\ 
  retail & -1.86 & 1.07 & -3.98 & -1.85 & 0.23 & FALSE & -1.74 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Apr  3 19:45:51 2024
\begin{table}[ht]
    \centering
    \begin{tabular}{rrrrrrlr}
      \hline
     & mean & sd & 2.5\% & 50\% & 97.5\% & sig & abs\_Z \\ 
      \hline
    intercept & 3.68 & 0.51 & 2.68 & 3.68 & 4.69 & TRUE & 7.20 \\ 
      seasonSpring & -0.07 & 0.08 & -0.23 & -0.07 & 0.10 & FALSE & -0.78 \\ 
      seasonSummer & -0.55 & 0.09 & -0.72 & -0.55 & -0.38 & TRUE & -6.35 \\ 
      seasonWinter & -0.23 & 0.09 & -0.41 & -0.23 & -0.05 & TRUE & -2.55 \\ 
      BC & 0.82 & 0.16 & 0.51 & 0.82 & 1.14 & TRUE & 4.98 \\ 
      M & -1.92 & 0.92 & -3.75 & -1.91 & -0.11 & TRUE & -2.08 \\ 
      NB & -2.63 & 1.05 & -4.72 & -2.63 & -0.57 & TRUE & -2.51 \\ 
      NL & -3.08 & 1.11 & -5.31 & -3.06 & -0.89 & TRUE & -2.77 \\ 
      NT & -5.41 & 1.27 & -7.92 & -5.39 & -2.91 & TRUE & -4.24 \\ 
      NS & -2.42 & 1.00 & -4.39 & -2.41 & -0.46 & TRUE & -2.43 \\ 
      N & -5.01 & 1.27 & -7.52 & -5.01 & -2.53 & TRUE & -3.94 \\ 
      O & 5.61 & 2.45 & 0.80 & 5.59 & 10.51 & TRUE & 2.29 \\ 
      PEI & -4.13 & 1.22 & -6.54 & -4.12 & -1.73 & TRUE & -3.39 \\ 
      Q & 2.20 & 0.93 & 0.36 & 2.19 & 4.07 & TRUE & 2.35 \\ 
      S & -2.59 & 0.94 & -4.46 & -2.57 & -0.75 & TRUE & -2.74 \\ 
      Y & -4.15 & 1.25 & -6.61 & -4.14 & -1.71 & TRUE & -3.33 \\ 
      retail & -1.86 & 1.07 & -3.98 & -1.85 & 0.23 & FALSE & -1.74 \\ 
       \hline
    \end{tabular}
    \end{table}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Apr  3 19:45:51 2024
\begin{table}[ht]
    \centering
    \begin{tabular}{rrrrrrlr}
      \hline
     & mean & sd & 2.5\% & 50\% & 97.5\% & sig & abs\_Z \\ 
      \hline
    intercept & 3.00 & 0.21 & 2.58 & 3.01 & 3.42 & TRUE & 14.18 \\ 
      seasonSpring & -0.04 & 0.01 & -0.07 & -0.04 & -0.03 & TRUE & -4.59 \\ 
      seasonSummer & -0.55 & 0.01 & -0.56 & -0.55 & -0.54 & TRUE & -80.24 \\ 
      seasonWinter & -0.20 & 0.01 & -0.23 & -0.20 & -0.18 & TRUE & -16.63 \\ 
      BC & 0.67 & 0.05 & 0.57 & 0.67 & 0.76 & TRUE & 13.97 \\ 
      M & -0.67 & 0.39 & -1.43 & -0.68 & 0.10 & FALSE & -1.73 \\ 
      NB & -1.21 & 0.44 & -2.08 & -1.22 & -0.33 & TRUE & -2.76 \\ 
      NL & -1.56 & 0.47 & -2.49 & -1.57 & -0.62 & TRUE & -3.34 \\ 
      NT & -3.68 & 0.52 & -4.70 & -3.68 & -2.63 & TRUE & -7.01 \\ 
      NS & -1.07 & 0.42 & -1.89 & -1.08 & -0.23 & TRUE & -2.57 \\ 
      N & -3.30 & 0.53 & -4.33 & -3.30 & -2.24 & TRUE & -6.27 \\ 
      O & 2.24 & 1.05 & 0.14 & 2.25 & 4.29 & TRUE & 2.14 \\ 
      PEI & -2.47 & 0.51 & -3.48 & -2.48 & -1.45 & TRUE & -4.85 \\ 
      Q & 0.92 & 0.40 & 0.13 & 0.92 & 1.69 & TRUE & 2.32 \\ 
      S & -1.31 & 0.40 & -2.09 & -1.32 & -0.52 & TRUE & -3.32 \\ 
      Y & -2.46 & 0.52 & -3.49 & -2.47 & -1.41 & TRUE & -4.70 \\ 
      retail & -0.39 & 0.45 & -1.29 & -0.40 & 0.52 & FALSE & -0.87 \\ 
       \hline
    \end{tabular}
    \end{table}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Apr  3 19:45:51 2024
\begin{table}[ht]
    \centering
    \begin{tabular}{rrrrrrlr}
      \hline
     & mean & sd & 2.5\% & 50\% & 97.5\% & sig & abs\_Z \\ 
      \hline
    intercept & 3.66 & 0.05 & 3.56 & 3.66 & 3.76 & TRUE & 69.93 \\ 
      seasonSpring & -0.07 & 0.01 & -0.09 & -0.07 & -0.04 & TRUE & -5.54 \\ 
      seasonSummer & -0.56 & 0.02 & -0.59 & -0.56 & -0.53 & TRUE & -34.43 \\ 
      seasonWinter & -0.24 & 0.01 & -0.27 & -0.24 & -0.21 & TRUE & -17.13 \\ 
      BC & 0.82 & 0.02 & 0.78 & 0.82 & 0.86 & TRUE & 38.66 \\ 
      M & -1.89 & 0.09 & -2.07 & -1.89 & -1.71 & TRUE & -20.33 \\ 
      NB & -2.61 & 0.11 & -2.83 & -2.61 & -2.40 & TRUE & -23.98 \\ 
      NL & -3.07 & 0.12 & -3.30 & -3.07 & -2.83 & TRUE & -25.26 \\ 
      NT & -5.20 & 0.28 & -5.80 & -5.18 & -4.70 & TRUE & -18.50 \\ 
      NS & -2.40 & 0.10 & -2.60 & -2.40 & -2.20 & TRUE & -23.24 \\ 
      N & -4.96 & 0.25 & -5.50 & -4.95 & -4.51 & TRUE & -19.51 \\ 
      O & 5.54 & 0.24 & 5.07 & 5.54 & 6.02 & TRUE & 23.00 \\ 
      PEI & -4.16 & 0.18 & -4.51 & -4.15 & -3.83 & TRUE & -23.76 \\ 
      Q & 2.17 & 0.09 & 1.99 & 2.17 & 2.35 & TRUE & 23.50 \\ 
      S & -2.58 & 0.10 & -2.78 & -2.57 & -2.38 & TRUE & -25.32 \\ 
      Y & -4.18 & 0.17 & -4.54 & -4.18 & -3.85 & TRUE & -24.19 \\ 
      retail & -1.82 & 0.10 & -2.03 & -1.82 & -1.62 & TRUE & -17.41 \\ 
       \hline
    \end{tabular}
    \end{table}
